Active Learning for Level Set Estimation

### 2013-03-24 figurefactory/proof.tex
Small fixes

@@

 \node[st,left=2em of amb] (t0) {Monotonicity}
   edge[pil] (amb);
 \node[st,left=3em of dummy] (t1) {Samples ($t$)}
   edge[pil] (amb);
 \node[st,right=1em of t1] (t2) {Kernel ($k$)}
   edge[pil] (amb);
 \node[st,right=1em of t2] (t3) {Noise ($\sigma$)}
   edge[pil] (amb);
 \node[st,right=3em of t3] (t4) {$\beta_t$}
   edge[pil] (amb);

@@

 \node[st,right=2em of loss] (rules) {Classification rules}
   edge[pil] (loss);

@@

 \node[st,right=1.5em of clas] (eps) {$\epsilon$}
   edge[pil] (amb)
   edge[pil] (loss);
\end{tikzpicture}
\end{document}

>>>>

\definecolor{col1}{RGB}{140,191,38}

@@

 \node[st,left=2em of amb] (t0) {Monotonicity}
   edge[pil] (amb);
 \node[st,left=3em of dummy] (t1) {Samples ($t$)}
   edge[pil] (amb);
 \node[st,right=1em of t1] (t2) {Kernel ($k$)}
   edge[pil] (amb);
 \node[st,right=1em of t2] (t3) {Noise ($\sigma$)}
   edge[pil] (amb);
 \node[st,right=3em of t3,fill=col1] (t4) {$\beta_t$}
   edge[pil] (amb);

@@

 \node[st,right=2em of loss] (rules) {Class. rules}
   edge[pil] (loss);

@@

 \node[st,right=1.5em of clas,fill=col1] (eps) {$\epsilon$}
   edge[pil] (amb)
   edge[pil] (loss);
\end{tikzpicture}
\end{document}
